Matching the Time of Emergence of Transboundary Fish Stocks to Lead Time for

### 2020-05-25 Scripts/Initial_Analysis.Rmd
Fixing Nas issues

  # Future results
  future <- Centroids_id %>% 
    filter(year > Hist_y)

@@

  Partial <- Trans_index %>% 
    mutate(
      names = ifelse(eez_name ==Unique_EEZs[1],paste("Country_A",variable,sep="_"),paste("Country_B",variable,sep="_"))
    ) %>%
    select(-eez_name,-variable) %>%
    spread(names,value) %>% 
    # mutate index
    mutate(
      trans_index = (Country_A_distance/Country_A_hd_temp_sd - Country_B_distance/Country_B_hd_temp_sd)^2
    ) %>% 
    # Ten years average of results
    group_by(taxon_key,ensemble,neighbour_id) %>% 
    mutate(RMean = rollmean(x = trans_index, 
                            10, 
                            align = "right", 
                            fill = trans_index)
    ) %>% 
    filter(year > 1960) %>% 
    select(taxon_key,neighbour_id,year,ensemble,trans_index,RMean)

@@

    # First step
    # Call Get centroids fucntion for centroids data per ensemble
    Step_one <- bind_rows(
      lapply(ensemble_list[1:2],
             GetCentroids,
             taxon_key = taxon_key,
             year = year_df$year,
             data_type = data_type,
             Neighbours = Neighbours,
             eez_centroid = eez_centroid
             )
    )

@@

    # Second Step
    # Get the transboudary index based on all centroids
    Step_two <- bind_rows(
      lapply(Ids,
             TransIndex,
             Hist_y = Hist_y,
             Centroid = Step_one)
    )

@@

#  List os species
spp_list <- unique(Transboundary_spp$taxon_key)[1:2]

@@

suppressMessages(
  suppressWarnings(
    Emerging_result <- bind_rows(
      mclapply(spp_list[1],
               GetTransIndex,
               year = year_df$year,
               Hist_y = Historic_year,
               data_type = "Catch",
               ensemble_list = ensemble_list,
               # path = path,
               Neighbours = Neighbours,
               eez_centroid = eez_centroid
      )
    )
  )
)

@@

write_csv(Emerging_result,
          "~/Desktop/Test.csv")

>>>>

  # Future results
  future <- Centroids_id %>% # FIX ME CUS I PRODUCE A BUNCH OF NAs WITH SSP 600076 ENS 102 AND 104
    filter(year > Hist_y)

@@

  Partial <- Trans_index %>% 
    mutate(
      names = ifelse(eez_name ==Unique_EEZs[1],paste("Country_A",variable,sep="_"),paste("Country_B",variable,sep="_"))
    ) %>%
    # Filter out ensembels that have no data
    filter(!is.na(value)) %>% 
    select(-eez_name,-variable) %>%
    spread(names,value) %>% 
    # mutate index
    mutate(
      trans_index = (Country_A_distance/Country_A_hd_temp_sd - Country_B_distance/Country_B_hd_temp_sd)^2
    ) %>% 
    # Ten years average of results
    group_by(taxon_key,ensemble,neighbour_id) %>% 
    mutate(RMean = rollmean(x = trans_index, 
                            10, 
                            align = "right", 
                            fill = trans_index)
    ) %>% 
    filter(year > 1960) %>% 
    select(taxon_key,neighbour_id,year,ensemble,trans_index,RMean)

@@

    # First step
    # Call Get centroids fucntion for centroids data per ensemble
    Step_one <- bind_rows(
      lapply(ensemble_list,
             GetCentroids,
             taxon_key = taxon_key,
             year = year_df$year,
             data_type = data_type,
             Neighbours = Neighbours,
             eez_centroid = eez_centroid
             )
    )

@@

    # Second Step
    # Get the transboudary index based on all centroids
    Step_two <- bind_rows(
      lapply(Ids[7],
             TransIndex,
             Hist_y = Hist_y,
             Centroid = Step_one)
    )

@@

@@

suppressMessages(
  suppressWarnings(
    Emerging_result <- bind_rows(
      mclapply(spp_list,
               GetTransIndex,
               year = year_df$year,
               Hist_y = Historic_year,
               data_type = "Catch",
               ensemble_list = ensemble_list,
               Neighbours = Neighbours,
               eez_centroid = eez_centroid
      )
    )
  )
)

@@

write_csv(Emerging_result,
          paste(my_path("R"),"Emerging_Results.csv",sep="")
)
